\section*{\LARGE{Projects}}
\begin{multicols}{2}
    \begin{description}
        \item \textbf{Android}
        \begin{itemize}
            \item \href{https://github.com/yamin8000/PrettyPersianNumbers}{\textbf{PrettyPersianNumbers}}\\
            I created an Android library to convert a number to a word for Persian/Farsi using Kotlin/JVM
            and published it to maven repository.
            \item \href{https://github.com/yamin8000/Dooz}{\textbf{Dooz}}\\
            A simple pen-and-paper game.
            I created this implementation using Kotlin and Jetpack Compose for Android devices.
            \item \href{https://github.com/yamin8000/freeDictionaryApp}{\textbf{freeDictionaryApp}}
            A simple android application for freeDictionaryAPI, published in F-Droid and CafeBazaar.
            \item \href{https://github.com/yamin8000/Gauge}{\textbf{Gauge}}\\
            A fusion of classic and modern Gauges with some customization options for Jetpack Compose.
        \end{itemize}
        \item \textbf{Web}
        \begin {itemize}
            \item \href{https://andro.law}{\textbf{Androlaw}}\\
            I was part of a three-man group that designed and implemented this website.
            I helped in design and implementation of various pages on this website using Laravel, Blade, Bootstrap, and Javascript.
            My work included but not limited to implementing various controllers/services using PHP, designing front-end pages using Blade/HTML/CSS/JavaScript and bootstrap.
            \item \href{https://ansp.ir}{\textbf{ansp.ir}}\\
            I helped in the design and development of the site back-end and databases,
            using .NET Core and PostgreSQL\@.
        \end{itemize}
        \item \textbf{IoT}
        \begin{itemize}
            \item \href{https://hirkaniafaratech.ir/2024-01-04/mehran/252}{\textbf{Monex}}\\
            I designed and implemented an Android App used as the interface of the Monex device.
            The app is implemented using Kotlin and Jetpack Compose UI and communicates with an Arduino device with USB Serial.
        \end{itemize}
        \item \textbf{JVM(Java, Kotlin)}
        \begin{itemize}
            \item \href{https://github.com/yamin8000/coinex4j}{coinex4j}\\
            CoinEx Exchange API JVM Library created with help of the Retrofit library.
            \item \href{https://github.com/TradersTeam/grand-node-java-client}{grand-node-java-client}\\
            A JVM client for GrandNode2 API powered by Retrofit and Project Lombok.
            \item \href{https://github.com/yamin8000/SpaceTradersKMP}{SpaceTradersKMP}\\
            SpaceTraders API wrapper for Kotlin Multiplatform (https://spacetraders.io/).
            \item \href{https://github.com/yamin8000/InstaCLI}{InstaCLI}\\
            A CLI client for Instagram created using Retrofit, instagram4j, jackson and Kotlin Coroutines.
            \item \href{https://github.com/yamin8000/TwitterScrapper}{TwitterScrapper}\\
            A simple CLI tool for scrapping Tweets from Nitter without authentication
        \end{itemize}
        \item \href{https://github.com/yamin8000}{\textbf{Other projects}}
        \begin{itemize}
            \item Github: \href{https://github.com/yamin8000}{https://github.com/yamin8000}
        \end{itemize}
    \end{description}
\end{multicols}